\chapter{Literature Review}

\cite{DetectionMultiplMagnetiDipoleSources} 
This article proposes a new method to simultaneously estimate the locations and magnetic 
moments of multiple magnetic dipole sources without the prior knowledge of the number of 
dipoles in the 3-D detection region. By initializing a large number of dipole sources 
evenly spaced in the detection region as potential candidates for the true dipoles, we 
introduce an indicator parameter for each dipole candidate such that its Sigmoid function 
is the probability that the candidate converges to a true dipole. A joint optimization is 
then formulated to minimize the mean square of the regularized error between the measured 
magnetic gradients and the calculated gradients from the estimated dipoles. The proposed 
nonlinear optimization is solved by the Levenberg–Marquardt algorithm, yielding the 
indicators and their corresponding dipole locations and magnetic moments. \\
 
\cite{multiple_in_spacecraft} 
Multi-magnetic source resolution in spacecraft has been a difficult problem in the field 
of magnetic surveys. Detection technology of magnetic gradient tensor is available to 
solve this issue due to its high resolution and precision. A spacecraft magnetic source 
model is established, and a multi-magnetic source model fitting method for spacecraft is 
presented. The principal invariants of the magnetic field gradient tensor are introduced 
to determine the number and horizontal location of the sources, while Euler equations are 
used to compute the source depth, achieving a resolution of up to 0.012m, which meets 
engineering requirements. \\

\cite{real_application} 
Nothing much is a real application. \\

\cite{multiple_plots} 
Questo è il paper utile dove ci sono tutti i plot. \\

\cite{multiple_DE_NSS_big_matrix} 
This article presents a new method for detecting and localizing multiple dipole-like 
magnetic sources using magnetic gradient tensor data. The tilt angle (ratio of vertical 
to horizontal magnetic field components) is used to determine the number of sources, 
while the rotational-invariant normalized source strength (NSS) is used to estimate the 
horizontal coordinates. The Differential Evolution (DE) algorithm estimates the 
locations and moments of the sources. \\

\cite{single_closed_formula_position} 
This paper presents a simple formula for the localization of a magnetic dipole. First, 
the position vector is derived from the analytical expressions of the magnetic field 
vector and the magnetic gradient tensor. The proposed algorithm provides the true 
position of the dipole regardless of the singularity of the magnetic gradient tensor 
matrix. \\

\cite{multiple_real_plots_invariants} 
This paper proposes a new edge detection method using magnetic gradient tensor components 
for magnetic exploration, which is free from geomagnetic interference and provides 
abundant information. The method is compared with others, such as THDz, AS, tilt angle, 
and theta map, under various conditions. The experimental results show that the proposed 
method is more precise and delivers high-quality edge detection with strong 
anti-interference capabilities. \\

\cite{NSS_formula_important} 
This paper proposes a two-point magnetic gradient tensor localization model to overcome 
errors caused by geomagnetic fields. The model uses the spatial relation between the 
magnetic target and observation points derived from tensor invariants. A new method is 
presented for accurately locating magnetic targets, achieving nearly error-free results 
in the absence of noise. \\

\cite{NSS_single_different_dimensions} 
This paper introduces new methods for inverting magnetic gradient tensor data to obtain 
source parameters for various models, such as dipoles and thin sheets. Eigenvalues and 
eigenvectors of the tensor are used in combination with normalized source strength (NSS) 
to uniquely determine source locations. NSS analysis is extended to vertical pipes by 
calculating eigenvalues of the vertical derivative of the tensor. \\

\cite{NSS_single_localization} 
This article introduces a novel magnetic dipole localization method based on normalized 
source strength (NSS) to overcome asphericity errors in magnetic anomaly detection (MAD). 
A closed-form localization formula is derived, and an optimization method is proposed to 
improve noise immunity. Simulation and field experiments demonstrate high localization 
accuracy, real-time performance, and robustness against noise and misalignment errors. \\

\cite{NSS_analysis} 
For a number of widely used models, normalized source strength (NSS) can be derived from 
eigenvalues of the magnetic gradient tensor. NSS is proportional to a constant normalized 
by the distance between observation and integration points. It is independent of 
magnetization direction and satisfies Euler’s homogeneity equation, allowing for Euler 
deconvolution of the NSS to estimate source location. The method was applied to 
aeromagnetic data from the Tuckers Igneous Complex, Queensland, Australia, improving the 
interpretation of magnetic anomalies with strong remanent magnetization. \\

\cite{not_import_formula_z} 
Closed loop formula to find z. \\

\cite{NSS_analysis2} 
Recent technological advances suggest that we are on the threshold of a new era in 
applied magnetic surveys, where acquisition of magnetic gradient tensor data will become 
routine. In the meantime, modern ultrahigh resolution conventional magnetic data can be 
used, with certain important caveats, to calculate gradient tensor elements from total 
magnetic intensity (TMI) or TMI gradient surveys. Until the present, not a great deal of 
attention has been paid to processing and interpretation of gradient tensor data. New 
methods for inverting gradient tensor surveys to obtain source parameters have been 
developed for a number of elementary, but useful, models. These include point pole, line 
of poles, point dipole (sphere), line of dipoles (horizontal cylinder), thin and thick 
dipping sheets, sloping step, and contact models. A key simplification is the use of 
eigenvalues and associated eigenvectors of the tensor. The scaled source strength, 
calculated from the eigenvalues, is a particularly useful rotational invariant that peaks 
directly over compact sources, 2D sources, and contacts, independent of magnetization 
direction. New algorithms for uniquely determining the location and magnetic moment of a 
dipole source from a few irregularly located measurements or single profiles have been 
developed. Besides geological applications, these algorithms are readily applicable to 
the detection, location, and classification (DLC) of magnetic objects, such as naval 
mines, UXO, shipwrecks, archaeological artifacts, and buried drums. As an example, some 
of these new methods are applied to analysis of the magnetic signature of the Mount 
Leyshon gold-mineralized system, Queensland. \\

\cite{PSO_IMPORTANT} 
In this paper, a modified particle swarm optimization (PSO) algorithm is developed for 
solving multimodal function optimization problems. The difference between the proposed 
method and the general PSO is to split up the original single population into several 
subpopulations according to the order of particles. The best particle within each 
subpopulation is recorded and then applied into the velocity updating formula to replace 
the original global best particle in the whole population. To update all particles in 
each subpopulation, the modified velocity formula is utilized. Based on the idea of 
multiple subpopulations, for the multimodal function optimization, several optima 
including the global and local solutions may be found by these best particles 
separately. To show the efficiency of the proposed method, two kinds of function 
optimizations are provided, including a single modal function optimization and a complex 
multimodal function optimization. Simulation results will demonstrate the convergence 
behavior of particles by the number of iterations, and the global and local system 
solutions are solved by these best particles of subpopulations.